---
title: "Danaher's marker output"

output:
  html_document:
  df_print: paged
---

```{r setup, include=FALSE}
source("danaher.R")
```

## R Markdown

This is an result for the gene singatures as well as assigned cell type for each cluster based on Danaher et al. 

```{r }
knitr::opts_chunk$set(cache=TRUE)
for( i in 1:length(mean_score[1,])){
print(visualize_me(mean_score[,i],cell_list[i],analysis_results$tsne[c("TSNE.1","TSNE.2")],title=names(cell_list)[i]))
# really hard to see
#print(plot(mean_score[,i],type = "h",xlab="Single Cell",ylab=colnames(mean_score)[i]))
h <-hist(mean_score[,i],plot = FALSE)

print(plot(h, freq = TRUE, labels =TRUE, ylim=c(0, 1.2*max(h$counts)),main=c(names(cell_list)[i]," Score per Single Cell"),xlab=paste(sep=" ",names(cell_list)[i],"Expression Level"),ylab="Numbers of cells"))
}
sig_plot <- visualize_clusters(cluster_tsne$cell_type,cluster_tsne[c("TSNE.1","TSNE.2")],title="Danaher cell-type labels",legend_anno= sort(unique(cluster_tsne[,"name_type"])))
#sig_plot <-sig_plot +scale_fill_discrete(name="Cell Type",
#                         breaks=unique(cluster_assignment$cell_type),
#                         labels=sapply(unique(cluster_assignment$cell_type),function(x) names(cell_list[x])))

print(sig_plot)

counter <-1
colnames(score_by_cluster) <- names(cell_list)
apply(score_by_cluster, 1,function(x) {plot(x,ylab="mean expression level",xlab="cell type", main=c("Cluster",counter))
text(x, names(cell_list), cex=0.6, pos=4, col="red")
counter <<- counter + 1})


```


This is a gene exprssion profile for each cell signature for each custer.The top expressed gene signatures of the majority of the cluster are well reprsented (All signatures are expressed among 80% to 90% of the cells in each  cluster, except in Cluster 4,5 and 9)    
```{r ,paged.print=TRUE }
top_sig <- data.frame(t(sapply(unique(all_type_expr_table$Cluster),function(x){ all_type_expr_table[all_type_expr_table$Cluster == x,][which(all_type_expr_table$precent_count[all_type_expr_table$Cluster == x] == max(all_type_expr_table$precent_count[all_type_expr_table$Cluster == x])),] })))
top_sig$Signature <-lapply(top_sig$Signature,function(y){paste(y)})
cbind(top_sig, cluster_assignment = cluster_type[,"name_type"])
top_sig
all_type_expr_table
```
A closer look at gene composition in Cluster 7 (used as an example). PCA is performed for Cytotoxic_cells to determine which gene(s) "drive" the signature. Excluding cell with only zeor counts. Furhter Normalization is required - Need to work on that.  
```{r}
knitr::opts_chunk$set(cache=TRUE)
all_list_gene<- get_signature_matrix (all_type_expr,7,"Cytotoxic_cells")
alg_pca<-prcomp(all_list_gene)
summary(alg_pca)
plot(alg_pca, type = "l")
alg_pca
loadings <- alg_pca$rotation
sdev <- alg_pca$sdev
var_coord <- var.cor <- t(apply(loadings, 1, var_cor_func, sdev))

test_1 <- all_type_expr[ all_type_expr$Cluster==7 & all_type_expr$Signature =="Cytotoxic_cells",] %>% group_by(Gene,Signature) %>% summarise(count=n_distinct(Barcode),EXP_mean=mean(as.numeric(Expression)),SD_mean = sd(as.numeric(Expression)),Abs_Exp=sum(as.numeric(Expression)))
test_1
```
