---
title: "Danaher's marker output"

output:
  html_document:
  df_print: paged
---

```{r setup, include=FALSE}
source("danaher.R")
library(knitr)
```

## Cluster Analysis 

### Most Expressed Signature among clusters 
This is a gene exprssion profile for each cell signature for each custer.The most expressed gene signatures of the majority of the cluster are well reprsented (All signatures are expressed among 80% to 90% of the cells in each  cluster, except in Cluster 4,5 and 9)
```{r ,paged.print=TRUE }
top_sig <- data.frame(t(sapply(unique(all_type_expr_table$Cluster),function(x){ all_type_expr_table[all_type_expr_table$Cluster == x,][which(all_type_expr_table$precent_count[all_type_expr_table$Cluster == x] == max(all_type_expr_table$precent_count[all_type_expr_table$Cluster == x])),] })))
top_sig$Signature <-lapply(top_sig$Signature,function(y){paste(y)})
top_sig$Cluster <-unique(unlist(top_sig$Cluster))
kable(merge(x=top_sig, y=cluster_type[,c("Cluster","name_type")],by="Cluster"))
cat("\n")
```
## Principal Component Analysis
A closer look at gene composition in Cluster 7 (used as an example). PCA is performed for Cytotoxic_cells to determine which gene(s) "drive" the signature. Excluding cell with only zeor counts. Furhter Normalization is required - Need to work on that. PCA result(1st +2nd compoenet) seems to be consistent with Absolute Expression of each genes-NKG7 and GNLY are the most expressed genes in Cluster 7 and clustered seperately from the PCA 1/2 results (uncertain)
```{r,paged.print=TRUE}
knitr::opts_chunk$set(cache=TRUE)

test_1 <- all_type_expr[ all_type_expr$Cluster==7 & all_type_expr$Signature =="Cytotoxic_cells",] %>% group_by(Gene,Signature) %>% summarise(count=n_distinct(Barcode),EXP_mean=mean(as.numeric(Expression)),SD_mean = sd(as.numeric(Expression)),Abs_Exp=sum(as.numeric(Expression)))
gene_name <- gen[match(unlist(test_1[,1]),gen$id),]$symbol
kable(cbind(test_1,gene = gene_name))
print("\n")

all_list_gene<- get_signature_matrix (all_type_expr,7,"Cytotoxic_cells")
colnames(all_list_gene) <- gen[match(unlist(colnames(all_list_gene)),gen$id),]$symbol
alg_pca<-prcomp(all_list_gene)
plot(alg_pca, type = "l")
alg_pca$rotation
loadings <- alg_pca$rotation
x = loadings[,1]
y = loadings[,2]
hc = hclust(dist(cbind(x,y)), method = 'ward.D2')
plot(hc, axes=F,xlab='', ylab='',sub ='', main='Comp 1/2')
sum_alg_pca <- summary(alg_pca)
sum_alg_pca
```
